Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study

### 2024-11-19 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
updated R script

# Annotated Plot
plot_gri_group <- df_gri %>%
  ggplot(aes(x = Group, y = GRI, fill = Group)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(size = 2, alpha = 0.7, width = 0.1, height = 0.1, seed = 1) +
  ylim(0, y_max_gri) +
  labs(x = "", y = "Average Duration of Fixations /\nNumber of Fixations per Minute") +
  scale_fill_brewer(palette = "RdBu") +
  ggtitle("GRI\n(Micro-Teaching Unit)") +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, face = "bold")
  ) +
  # Annotate mean (M) and SD
  annotate("text", x = 1, y = y_max_gri * 0.85,
           label = paste0("atop(italic(M) == ", mean_novice_gri, ", italic(SD) == ", sd_novice_gri, ")"),
           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
  annotate("text", x = 2, y = y_max_gri * 0.85,
           label = paste0("atop(italic(M) == ", mean_expert_gri, ", italic(SD) == ", sd_expert_gri, ")"),
           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
  # Annotate p-value and Cohen's d
  annotate("text", x = 1.5, y = y_max_gri * 0.95,
           label = paste0("p = ", p_value_gri, "\nd = ", d_gri),
           hjust = 0.5, size = 4, fontface = "italic")

@@

# read in data and combine multiple excel sheets into a single table 
sri <-
  excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201),
    !disruption_appraisal == -100,
    !confidence_appraisal == -100,
    !disruption_appraisal == -99,
    !confidence_appraisal == -99,
    !disruption_appraisal == -88,
    !confidence_appraisal == -88,
    !prevalence_rating == -100,
    !prevalence_rating == -99,
    !prevalence_rating == -88
    ) %>%
  mutate(ID = ifelse(ID < 200, "Novice", "Expert"))

############## Disruption appraisal #########################

sri.disrup.table <-
  sri %>%
  group_by(ID) %>%
  summarise(
    N = n(),
    "M" = round(mean(disruption_appraisal), digits = 2),
    "SD" = round(sd(disruption_appraisal), digits = 2),
    "Min" = min(disruption_appraisal),
    "Max" = max(disruption_appraisal)
    )

knitr::kable(sri.disrup.table,
             caption = "Disruption Appraisal")

### with event
sri.disrup.event.table <-
  sri %>%
  group_by(ID, event) %>%
  summarise(
    N = n(),
    "M" = round(mean(disruption_appraisal), digits = 2),
    "SD" = round(sd(disruption_appraisal), digits = 2),
    "Min" = min(disruption_appraisal),
    "Max" = max(disruption_appraisal)
  )

# insert a table into HTML
knitr::kable(sri.disrup.event.table,
             caption = "Disruption appraisal with event")

# create a new data frame with appraisal
sri_disrup <- subset.data.frame(sri, select = c(ID, event, disruption_appraisal))

# plotting disruption appraisal for groups
dist_group_plot <- 
  sri_disrup %>% 
  mutate(ID = factor(ID,
                     levels = c("Novice",
                                "Expert"
                                )
                     )
         ) %>% 
  ggplot(mapping = aes(x = ID,
                       y = disruption_appraisal)) +
  geom_boxplot(mapping = aes(fill = ID),
               outlier.shape = NA) +
  geom_point(size = 1,
             alpha = 0.4,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  scale_x_discrete(limits = c("Novice", "Expert")) +
  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
  labs(x = "",
       y = "Disruption Appraisal") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("How disruptive was the event for you?") +
  theme_cowplot()

dist_group_plot
```

#### t-Test & effect size "Disruption appraisal"
```{r sri_da_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

#################### T-TEST & EFFECT SIZE ############

# Disruption appraisal 
# t-test for expertise differences
t.test(x = sri$disruption_appraisal[sri$ID == "Expert"],
       y = sri$disruption_appraisal[sri$ID == "Novice"],
       var.equal = TRUE)

# Disruption appraisal 
# effect size for expertise differences
d_sri_disrup <- CohenD(x = sri$disruption_appraisal[sri$ID == "Expert"],
                       y = sri$disruption_appraisal[sri$ID == "Novice"],
                       na.rm = TRUE)

round(d_sri_disrup, 2)
```

```{r sri_ca, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

############## Confidence appraisal #########################

sri.confi.table <-
  sri %>%
  group_by(ID) %>%
  summarise(
    "M" = round(mean(confidence_appraisal), digits = 2),
    "SD" = round(sd(confidence_appraisal), digits = 2),
    "Min" = min(confidence_appraisal),
    "Max" = max(confidence_appraisal)
  )

# insert a table into HTML
knitr::kable(sri.confi.table,
             caption = "Confidence appraisal")

### with event
sri.confi.event.table <- 
  sri %>%
  group_by(ID, event) %>%
  summarise(
    N = n(),
    "M" = round(mean(confidence_appraisal), digits = 2),
    "SD" = round(sd(confidence_appraisal), digits = 2),
    "Min" = min(confidence_appraisal),
    "Max" = max(confidence_appraisal)
  )

knitr::kable(sri.confi.event.table,
             caption = "Confidence appraisal with event")

# create a new data frame with appraisal
sri_confi <- subset.data.frame(sri, 
                               select = c(ID, 
                                          event, 
                                          confidence_appraisal)
                               )

# plotting confidence appraisal for groups
confi_group_plot <- 
  sri_confi %>% 
  mutate(ID = factor(ID,
                     levels = c("Novice",
                                "Expert"
                                )
                     )
         ) %>% 
  ggplot(mapping = aes(x = ID,
                       y = confidence_appraisal)) +
  geom_boxplot(mapping = aes(fill = ID),
               outlier.shape = NA) +
  geom_point(size = 1,
             alpha = 0.4,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  scale_x_discrete(limits = c("Novice", "Expert")) +
  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
  labs(x = "",
       y = "Confidence Appraisal") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("How confident did you feel dealing with this event?") +
  theme_cowplot()

confi_group_plot
```

#### t-Test & effect size "Confidence appraisal"
```{r sri_ca_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

#################### T-TEST & EFFECT SIZE ############

# Confidence Appraisal 
# t-test for expertise differences
t.test(x = sri$confidence_appraisal[sri$ID == "Expert"],
       y = sri$confidence_appraisal[sri$ID == "Novice"],
       var.equal = TRUE)

# Disruption Factor 
# effect size for expertise differences
d_sri_confi <- CohenD(x = sri$confidence_appraisal[sri$ID == "Expert"],
                      y = sri$confidence_appraisal[sri$ID == "Novice"],
                      na.rm = TRUE)

round(d_sri_confi, 2)
```

### Prevalence Rating as manipulation check
```{r sri_pr, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

############## Prevalence Rating #########################

sri.preva.table <-
  sri %>%
  group_by(ID) %>%
  summarise(
    N = n(),
    "M" = round(mean(prevalence_rating), digits = 2),
    "SD" = round(sd(prevalence_rating), digits = 2),
    "Min" = min(prevalence_rating),
    "Max" = max(prevalence_rating)
  )

knitr::kable(sri.preva.table,
             caption = "Prevalence rating")

sri.preva.event.table <-
  sri %>%
  group_by(ID, event) %>%
  summarise(
    N = n(),
    "M" = round(mean(prevalence_rating), digits = 2),
    "SD" = round(sd(prevalence_rating), digits = 2),
    "Min" = min(prevalence_rating),
    "Max" = max(prevalence_rating)
  )

knitr::kable(sri.preva.event.table,
             caption = "Prevalence rating with events")

sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))

preva_group_plot <- 
  sri_preva %>% 
  mutate(ID = factor(ID,
                     levels = c("Novice",
                                "Expert"
                                )
                     )
         ) %>% 
  ggplot(mapping = aes(x = ID,
                       y = prevalence_rating)) +
  geom_boxplot(mapping = aes(fill = ID),
               outlier.shape = NA) +
  geom_point(size = 1,
             alpha = 0.4,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  scale_x_discrete(limits = c("Novice", "Expert")) +
  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
  labs(x = "",
       y = "Prevalence Rating") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("How widespread is this event in the classroom?") +
  theme_cowplot()

preva_group_plot

#################### T-TEST & EFFECT SIZE ############

t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
       y = sri$prevalence_rating[sri$ID == "Novice"],
       var.equal = TRUE)

d_sri_preva <- CohenD(x = sri$prevalence_rating[sri$ID == "Expert"],
                      y = sri$prevalence_rating[sri$ID == "Novice"],
                      na.rm = TRUE)

round(d_sri_preva, 2)
```

### Internal consistency (Omega) for disruption and confidence appraisal
```{r sri_omega, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Select the relevant columns (e.g., Disruption Appraisal and Confidence Appraisal)
sri <-
  excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201),
    !disruption_appraisal == -100,
    !confidence_appraisal == -100,
    !disruption_appraisal == -99,
    !confidence_appraisal == -99,
    !disruption_appraisal == -88,
    !confidence_appraisal == -88,
    !prevalence_rating == -100,
    !prevalence_rating == -99,
    !prevalence_rating == -88
    )

# change long to wide format
sri_wide <- sri %>%
  pivot_wider(names_from = event, 
              values_from = c(disruption_appraisal, confidence_appraisal, prevalence_rating))

### DISRUPTIONS APPRAISAL

# create new data frame with only disruption items
sri_wide_disrup <- sri_wide %>%
  dplyr::select(starts_with("disruption_appraisal")) %>% 
  drop_na()

# calculate omega with omega() function  
omega_disrup <- omega(sri_wide_disrup)

# display the results 
print(omega_disrup)

### CONFIDENCE APPRAISAL

# create new data frame with only confidence items
sri_wide_confi <- sri_wide %>%
  dplyr::select(starts_with("confidence_appraisal")) %>% 
  drop_na()

# calculate omega with omega() function  
omega_confi <- omega(sri_wide_confi)

# display the results 
print(omega_confi)

@@

# read in data
df_sjt <- 
  read_excel("./data/SJT.xlsx")

# select relevant columns --> only subject ID and mean 
df_sjt <- df_sjt %>%
  dplyr::select(UI06_05, # ID
         SJT_AL_gek, # Monitoring
         SJT_ST_gek, # Managing momentum
         SJT_R_gek, # Rules and routines
         SJT_KF_gek) %>% # All
  filter(!UI06_05 == 201) # exclude ID with no eye tracking data

# remove NAs
df_sjt <- na.omit(df_sjt)

# rename columns
df_sjt <- rename(df_sjt, c("Group" = "UI06_05",
                           "Monitoring" = "SJT_AL_gek",
                           "Managing momentum" = "SJT_ST_gek",
                           "Rules and routines" = "SJT_R_gek",
                           "All" = "SJT_KF_gek"))

# changing from wide to long format
df_sjt_long <- df_sjt %>% 
  pivot_longer(!Group, names_to = "Facets Classroom Management", values_to = "Mean")

# define expert and novice with ifelse function
df_sjt_long$Group = ifelse(df_sjt_long$Group < 200, "Novice","Expert")

#################### N, MEAN & SD ############

# mean & SD SJT ALL
sjt_mean <- df_sjt_long %>%
  filter(`Facets Classroom Management` == "All") %>%
  group_by(Group) %>%
  summarise(N = n(),
            "M" = round(mean(Mean), 2),
            "SD" = round(sd(Mean), 2), 
            "Min" = round(min(Mean), 2),
            "Max" = round(max(Mean), 2), 
            )

# insert a table into HTML
knitr::kable(sjt_mean,
             caption = "N, M and SD for overall value")

# mean SJT Managing Momentum
sjt_mm <- df_sjt_long %>%
  filter(`Facets Classroom Management` == "Managing momentum") %>%
  group_by(Group) %>%
  summarise(N = n(),
            "M" = round(mean(Mean), 2),
            "SD" = round(sd(Mean), 2), 
            "Min" = round(min(Mean), 2),
            "Max" = round(max(Mean), 2), 
            )

# insert a table into HTML
knitr::kable(sjt_mm,
             caption = "N, M and SD for managing momentum")

# mean SJT Monitoring
sjt_m <- df_sjt_long %>%
  filter(`Facets Classroom Management` == "Monitoring") %>%
  group_by(Group) %>%
  summarise(N = n(),
            "M" = round(mean(Mean), 2),
            "SD" = round(sd(Mean), 2), 
            "Min" = round(min(Mean), 2),
            "Max" = round(max(Mean), 2), 
            )

# insert a table into HTML
knitr::kable(sjt_m,
             caption = "N, M and SD for monitoring")

# mean SJT Rules and routins
sjt_r <- df_sjt_long %>%
  filter(`Facets Classroom Management` == "Rules and routines") %>%
  group_by(Group) %>%
  summarise(N = n(),
            "M" = round(mean(Mean), 2),
            "SD" = round(sd(Mean), 2), 
            "Min" = round(min(Mean), 2),
            "Max" = round(max(Mean), 2), 
            )

# insert a table into HTML
knitr::kable(sjt_r,
             caption = "N, M and SD for rules and routines")

# plotting mean of all aspects 
mean_plot <- 
df_sjt_long %>% 
  mutate(Group = factor(Group,
                        levels = c("Novice", 
                                   "Expert")
                        )
         ) %>% 
  ggplot(mapping = aes(x = Group,
                       y = Mean)) +
  geom_boxplot(mapping = aes(fill = Group), 
               outlier.shape = NA) +
  geom_point(size = 1, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1,
                                        height = 0.1)) +
  labs(x = "") +
  ylim(0,1) + 
  scale_fill_brewer(palette  = "RdBu") +  
  facet_wrap(vars(`Facets Classroom Management`), 
             nrow = 1, strip.position = "bottom") +
  theme_cowplot() +
  ggtitle("SJT") +
    theme(
    plot.title = element_text(size = 25, 
                              face = "bold"),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_text(size = 8),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 22)
        )

mean_plot
```

#### t-test & effect size "STJ - All"
```{r sjt_all_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#################### T-TEST & EFFECT SIZE ##################

# define expert and novice with ifelse function in wide format
df_sjt$Group = ifelse(df_sjt$Group < 200, "Novice","Expert")

#### ALL #### 
# t-test for expertise differences 
t.test(x = df_sjt$All[df_sjt$Group == "Expert"],
       y = df_sjt$All[df_sjt$Group == "Novice"],
       var.equal = TRUE)

# effect size for expertise differences
d_sjt_all <- CohenD(x = df_sjt$All[df_sjt$Group == "Expert"],
                    y = df_sjt$All[df_sjt$Group == "Novice"],
                    na.rm = TRUE
                    )

round(d_sjt_all, 2)

#### t-test & effect size "SJT - Managing momentum"
```{r sjt_mm, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

#### MANAGING MOMENTUM #### 
# t-test for expertise differences 
t.test(x = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
       y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"],
       var.equal = TRUE
       )

# effect size for expertise differences
d_sjt_mm <- CohenD(x = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
                   y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"],
                   na.rm = TRUE
                  )

round(d_sjt_mm, 2)
```

#### t-test & effect size "SJT - Monitoring"
```{r sjt_m, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

#### MONITORING ####
# t-test for expertise differences 
t.test(x = df_sjt$Monitoring[df_sjt$Group == "Expert"],
       y = df_sjt$Monitoring[df_sjt$Group == "Novice"],
       var.equal = TRUE
       )

# effect size for expertise differences
d_sjt_moni <- CohenD(x = df_sjt$Monitoring[df_sjt$Group == "Expert"],
                     y = df_sjt$Monitoring[df_sjt$Group == "Novice"],
                     na.rm = TRUE
                    )

>>>>

# Annotated Plot
plot_gri_group <- df_gri %>%
  ggplot(aes(x = Group, y = GRI, fill = Group)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(size = 2, alpha = 0.7, width = 0.1, height = 0.1, seed = 1) +
  ylim(0, y_max_gri) +
  labs(x = "", y = "Average Duration of Fixations /\nNumber of Fixations per Minute") +
  scale_fill_brewer(palette = "RdBu") +
  ggtitle("GRI\n(Micro-Teaching Unit)") +
  theme_cowplot() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, face = "bold")
  ) +
  # Annotate mean (M) and SD
  annotate("text", x = 1, y = y_max_gri * 0.85,
           label = paste0("atop(italic(M) == ", mean_novice_gri, ", italic(SD) == ", sd_novice_gri, ")"),
           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
  annotate("text", x = 2, y = y_max_gri * 0.85,
           label = paste0("atop(italic(M) == ", mean_expert_gri, ", italic(SD) == ", sd_expert_gri, ")"),
           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
  # Annotate p-value and Cohen's d
  annotate("text", x = 1.5, y = y_max_gri * 0.95,
           label = paste0("p = ", p_value_gri, "\nd = ", d_gri),
           hjust = 0.5, size = 4, fontface = "italic")

@@

# Data Import and Preprocessing ------------------------------------------
sri <- excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201, 223),
    !disruption_appraisal %in% c(-100, -99, -88),
    !confidence_appraisal %in% c(-100, -99, -88),
    !prevalence_rating %in% c(-100, -99, -88)
  ) %>%
  mutate(ID = ifelse(ID < 200, "Novice", "Expert"))

# Descriptive Statistics -------------------------------------------------
## Disruption Appraisal
sri_disrup_table <- sri %>%
  group_by(ID) %>%
  summarise(
    N = n(),
    M = round(mean(disruption_appraisal, na.rm = TRUE), 2),
    SD = round(sd(disruption_appraisal, na.rm = TRUE), 2),
    Min = round(min(disruption_appraisal, na.rm = TRUE), 2),
    Max = round(max(disruption_appraisal, na.rm = TRUE), 2)
  )

## Confidence Appraisal
sri_confi_table <- sri %>%
  group_by(ID) %>%
  summarise(
    N = n(),
    M = round(mean(confidence_appraisal, na.rm = TRUE), 2),
    SD = round(sd(confidence_appraisal, na.rm = TRUE), 2),
    Min = round(min(confidence_appraisal, na.rm = TRUE), 2),
    Max = round(max(confidence_appraisal, na.rm = TRUE), 2)
  )

## Prevalence Rating
sri_preva_table <- sri %>%
  group_by(ID) %>%
  summarise(
    N = n(),
    M = round(mean(prevalence_rating, na.rm = TRUE), 2),
    SD = round(sd(prevalence_rating, na.rm = TRUE), 2),
    Min = round(min(prevalence_rating, na.rm = TRUE), 2),
    Max = round(max(prevalence_rating, na.rm = TRUE), 2)
  )

# APA-Conform Tables -----------------------------------------------------
kable(sri_disrup_table, caption = "Descriptive Statistics for Disruption Appraisal", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

kable(sri_confi_table, caption = "Descriptive Statistics for Confidence Appraisal", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

kable(sri_preva_table, caption = "Descriptive Statistics for Prevalence Rating", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

# t-Tests and Effect Sizes -----------------------------------------------
## Disruption Appraisal
disrup_ttest <- t.test(
  disruption_appraisal ~ ID, data = sri, var.equal = TRUE
)
disrup_d <- cohen.d(disruption_appraisal ~ ID, data = sri)

## Confidence Appraisal
confi_ttest <- t.test(
  confidence_appraisal ~ ID, data = sri, var.equal = TRUE
)
confi_d <- cohen.d(confidence_appraisal ~ ID, data = sri)

## Prevalence Rating
preva_ttest <- t.test(
  prevalence_rating ~ ID, data = sri, var.equal = TRUE
)
preva_d <- cohen.d(prevalence_rating ~ ID, data = sri)

# APA-Conform Tables for t-Tests and Effect Sizes ------------------------
disrup_stats <- tibble(
  Statistic = c("t-value", "df", "p-value", "Cohen's d"),
  Value = c(
    round(disrup_ttest$statistic, 2),
    round(disrup_ttest$parameter, 2),
    round(disrup_ttest$p.value, 3),
    round(disrup_d$estimate, 2)
  )
)

confi_stats <- tibble(
  Statistic = c("t-value", "df", "p-value", "Cohen's d"),
  Value = c(
    round(confi_ttest$statistic, 2),
    round(confi_ttest$parameter, 2),
    round(confi_ttest$p.value, 3),
    round(confi_d$estimate, 2)
  )
)

preva_stats <- tibble(
  Statistic = c("t-value", "df", "p-value", "Cohen's d"),
  Value = c(
    round(preva_ttest$statistic, 2),
    round(preva_ttest$parameter, 2),
    round(preva_ttest$p.value, 3),
    round(preva_d$estimate, 2)
  )
)

kable(disrup_stats, caption = "t-Test and Effect Size for Disruption Appraisal", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

kable(confi_stats, caption = "t-Test and Effect Size for Confidence Appraisal", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

kable(preva_stats, caption = "t-Test and Effect Size for Prevalence Rating", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

# Plotting ---------------------------------------------------------------
## Disruption Appraisal
disrup_plot <- sri %>%
  ggplot(aes(x = ID, y = disruption_appraisal, fill = ID)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
  labs(x = "", y = "Disruption Appraisal") +
  scale_fill_brewer(palette = "RdBu") +
  ggtitle("Disruption Appraisal by Group") +
  theme_cowplot() +
  theme(legend.position = "none") +
  annotate(
    "text", x = 1.5, y = max(sri$disruption_appraisal, na.rm = TRUE) * 1.2,
    label = paste0(
      "p = ", round(disrup_ttest$p.value, 3), ", d = ",
      round(disrup_d$estimate, 2)
    ),
    size = 4, hjust = 0.5, fontface = "italic"
  )

print(disrup_plot)

## Confidence Appraisal
confi_plot <- sri %>%
  ggplot(aes(x = ID, y = confidence_appraisal, fill = ID)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
  labs(x = "", y = "Confidence Appraisal") +
  scale_fill_brewer(palette = "RdBu") +
  ggtitle("Confidence Appraisal by Group") +
  theme_cowplot() +
  theme(legend.position = "none") +
  annotate(
    "text", x = 1.5, y = max(sri$confidence_appraisal, na.rm = TRUE) * 1.2,
    label = paste0(
      "p = ", round(confi_ttest$p.value, 3), ", d = ",
      round(confi_d$estimate, 2)
    ),
    size = 4, hjust = 0.5, fontface = "italic"
  )

print(confi_plot)

## Prevalence Rating
preva_plot <- sri %>%
  ggplot(aes(x = ID, y = prevalence_rating, fill = ID)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(size = 1.5, alpha = 0.6, width = 0.2, height = 0.1) +
  labs(x = "", y = "Prevalence Rating") +
  scale_fill_brewer(palette = "RdBu") +
  ggtitle("Prevalence Rating by Group") +
  theme_cowplot() +
  theme(legend.position = "none") +
  annotate(
    "text", x = 1.5, y = max(sri$prevalence_rating, na.rm = TRUE) * 1.2,
    label = paste0(
      "p = ", round(preva_ttest$p.value, 3), ", d = ",
      round(preva_d$estimate, 2)
    ),
    size = 4, hjust = 0.5, fontface = "italic"
  )

print(preva_plot)

# Omega Calculations -----------------------------------------------------
# Data Import ------------------------------------------------------------
sri <- excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201, 223), # Exclude specific IDs
    !disruption_appraisal %in% c(-100, -99, -88),
    !confidence_appraisal %in% c(-100, -99, -88),
    !prevalence_rating %in% c(-100, -99, -88)
  )

# Change Long Format to Wide Format --------------------------------------
sri_wide <- sri %>%
  pivot_wider(
    names_from = event,
    values_from = c(disruption_appraisal, confidence_appraisal, prevalence_rating)
  )

# Helper Function for Omega Calculation -----------------------------------
calculate_omega_total <- function(data, scale_name) {
  if (nrow(data) == 0 || ncol(data) == 0) {
    warning(paste("No valid data for", scale_name))
    return(NA)
  }

  # Try Omega Calculation
  result <- tryCatch(
    omega(data),
    error = function(e) {
      warning(paste("Omega calculation failed for", scale_name, ":", e$message))
      return(NULL)
    }
  )

  # Check if Result is Valid and Extract omega.tot
  if (is.null(result) || !"omega.tot" %in% names(result)) {
    warning(paste("Omega total not available for", scale_name))
    return(NA)
  }

  return(round(result$omega.tot, 2))
}

# Disruption Appraisal ---------------------------------------------------
sri_wide_disrup <- sri_wide %>%
  dplyr::select(starts_with("disruption_appraisal")) %>%
  mutate(across(everything(), ~ as.numeric(.))) %>%
  drop_na()

omega_total_disrup <- calculate_omega_total(sri_wide_disrup, "Disruption Appraisal")

# Confidence Appraisal ---------------------------------------------------
sri_wide_confi <- sri_wide %>%
  dplyr::select(starts_with("confidence_appraisal")) %>%
  mutate(across(everything(), ~ as.numeric(.))) %>%
  drop_na()

omega_total_confi <- calculate_omega_total(sri_wide_confi, "Confidence Appraisal")

# Prevalence Rating ------------------------------------------------------
sri_wide_preva <- sri_wide %>%
  dplyr::select(starts_with("prevalence_rating")) %>%
  mutate(across(everything(), ~ as.numeric(.))) %>%
  drop_na()

omega_total_preva <- calculate_omega_total(sri_wide_preva, "Prevalence Rating")

# APA-Conform Table ------------------------------------------------------
omega_table <- tibble(
  Measure = c("Disruption Appraisal", "Confidence Appraisal", "Prevalence Rating"),
  Omega_Total = c(omega_total_disrup, omega_total_confi, omega_total_preva)
)

# Display APA-Conform Table ----------------------------------------------
kable(omega_table, caption = "Internal Consistency (Omega Total) for Appraisal Measures", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

@@

# Data Import and Preprocessing ------------------------------------------
df_sjt <- read_excel("./data/SJT.xlsx") %>%
  dplyr::select(
    UI06_05,  # ID
    SJT_AL_gek, # Monitoring
    SJT_ST_gek, # Managing momentum
    SJT_R_gek,  # Rules and routines
    SJT_KF_gek  # All
  ) %>%
  filter(!UI06_05 == 201) %>% # Exclude specific ID
  na.omit() %>% # Remove NAs
  rename(
    Group = UI06_05,
    Monitoring = SJT_AL_gek,
    `Managing momentum` = SJT_ST_gek,
    `Rules and routines` = SJT_R_gek,
    All = SJT_KF_gek
  ) %>%
  mutate(Group = ifelse(Group < 200, "Novice", "Expert")) # Define groups

# Reshape Data to Long Format --------------------------------------------
df_sjt_long <- df_sjt %>%
  pivot_longer(
    !Group,
    names_to = "Facets Classroom Management",
    values_to = "Mean"
  )

# Descriptive Statistics Tables ------------------------------------------
## Function to Calculate Descriptive Stats
descriptive_stats <- function(data, facet) {
  data %>%
    filter(`Facets Classroom Management` == facet) %>%
    group_by(Group) %>%
    summarise(
      N = n(),
      M = round(mean(Mean), 2),
      SD = round(sd(Mean), 2),
      Min = round(min(Mean), 2),
      Max = round(max(Mean), 2),
      .groups = "drop"
    )
}

## Generate Tables
sjt_all <- descriptive_stats(df_sjt_long, "All")
sjt_mm <- descriptive_stats(df_sjt_long, "Managing momentum")
sjt_m <- descriptive_stats(df_sjt_long, "Monitoring")
sjt_r <- descriptive_stats(df_sjt_long, "Rules and routines")

## Display APA-Conform Tables
kable(sjt_all, caption = "Descriptive Statistics for Overall SJT Score") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

kable(sjt_mm, caption = "Descriptive Statistics for Managing Momentum") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

kable(sjt_m, caption = "Descriptive Statistics for Monitoring") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

kable(sjt_r, caption = "Descriptive Statistics for Rules and Routines") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

# Plotting SJT Facets ----------------------------------------------------
mean_plot <- df_sjt_long %>%
  mutate(Group = factor(Group, levels = c("Novice", "Expert"))) %>%
  ggplot(aes(x = Group, y = Mean)) +
  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 1,
    alpha = 0.4,
    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
  ) +
  labs(x = "", y = "Mean SJT Score") +
  scale_fill_brewer(palette = "RdBu") +
  facet_wrap(~`Facets Classroom Management`, nrow = 1, strip.position = "bottom") +
  theme_cowplot() +
  ggtitle("SJT Scores by Group") +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12),
    axis.title.y = element_text(size = 14),
    axis.text.x = element_text(size = 12)
  )

print(mean_plot)

# Statistical Tests ------------------------------------------------------
## Function to Perform t-Test and Effect Size
t_test_stats <- function(data, group_col, value_col, facet_name) {
  group_col <- ensym(group_col)  # Ensure proper quoting of group column
  value_col <- ensym(value_col)  # Ensure proper quoting of value column

  # Perform t-Test
  t_test <- t.test(
    formula = as.formula(paste0("`", quo_name(value_col), "` ~ ", quo_name(group_col))),
    data = data,
    var.equal = TRUE
  )

  # Calculate Cohen's d
  cohen_d <- CohenD(
    x = data %>% filter(!!group_col == "Expert") %>% pull(!!value_col),
    y = data %>% filter(!!group_col == "Novice") %>% pull(!!value_col)
  )

  tibble(
    `Facet` = facet_name,
    `t-value` = round(t_test$statistic, 2),
    `p-value` = round(t_test$p.value, 3),
    `Cohen's d` = round(cohen_d, 2)
  )
}

## Generate t-Test Tables
t_test_all <- t_test_stats(df_sjt, "Group", "All", "Overall")
t_test_mm <- t_test_stats(df_sjt, "Group", "Managing momentum", "Managing Momentum")
t_test_m <- t_test_stats(df_sjt, "Group", "Monitoring", "Monitoring")
t_test_r <- t_test_stats(df_sjt, "Group", "Rules and routines", "Rules and Routines")

## Combine Results into a Table
t_test_results <- bind_rows(t_test_all, t_test_mm, t_test_m, t_test_r)

## Display APA-Conform Table
kable(t_test_results, caption = "t-Test and Effect Sizes for SJT Facets") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

# Internal Consistency (Omega) -------------------------------------------
# Data Import
df_sjt <- read_excel("./data/SJT.xlsx")

# Subset Data for Each Scale ---------------------------------------------
## Managing Momentum
df_managing_momentum <- df_sjt %>%
  select(matches("^WT_S1|^WT_S2|^WT_S3|^WT_S4")) %>%
  na.omit()

## Monitoring
df_monitoring <- df_sjt %>%
  select(matches("^WT_S5|^WT_S6|^WT_S7|^WT_S8|^WT_S9")) %>%
  na.omit()

## Rules and Routines
df_rules_routines <- df_sjt %>%
  select(matches("^WT_S11|^WT_S12|^WT_S13|^WT_S14")) %>%
  na.omit()

## Overall Mean (All Items Combined)
df_overall <- df_sjt %>%
  select(matches("^WT_S")) %>%  # Select all items starting with "WT_S"
  na.omit()

# Calculate Omega Total for Each Scale -----------------------------------
## Helper Function for Omega Calculation
calculate_omega <- function(data, scale_name) {
  tryCatch({
    result <- omega(data)
    return(round(result$total$omega.tot, 2))  # Extract Omega Total
  }, error = function(e) {
    warning(paste("Omega calculation failed for", scale_name, ":", e$message))
    return(NA)
  })
}
